 

### 2023-05-11 appendix_2.1.Rmd
Final revisions to manuscript

```
\end{raggedright}

@@

Visual inspect of our data showed potential outliers, which may have arisen due to data entry mistakes, synchronization errors, and other sources. To address outliers, monthly observations of the outcome were arranged separately for each facility into a unique time series. The nonparametric Friedman’s super smoother regression estimator [@friedmanVariableSpanScatterplot1984] was applied to each time series to identify outlier observations and replace them through linear interpolation [@hyndmanAutomaticTimeSeries2008]. By considering outliers on a facility-by-facility basis, the data cleaning approach preserved extreme values that may habe reflected true variances in visit counts (for example, visits reported by a large, regional reference hospital) while addressing potential errors in data entry. Interpolated values were coerced to the nearest integer.

>>>>

\end{raggedright}

@@

Visual inspect of our data showed potential outliers, which may have arisen due to data entry mistakes, synchronization errors, and other sources. To address outliers, monthly observations of the outcome were arranged separately for each facility into a unique time series. The nonparametric Friedman’s super smoother regression estimator [@friedmanVariableSpanScatterplot1984] was applied to each time series to identify outlier observations and replace them through linear interpolation [@hyndmanAutomaticTimeSeries2008]. By considering outliers on a facility-by-facility basis, the data cleaning approach preserved extreme values that may have reflected true variances in visit counts (for example, visits reported by a large, regional reference hospital) while addressing potential errors in data entry. Interpolated values were coerced to the nearest integer.

### 2023-05-11 appendix_2.2.Rmd
Final revisions to manuscript

* **Region**: The region of Madagascar that contained the facility's catchment area. All facilities had a value for this variable.
* **District**: The district of Madagascar (2nd largest administrative unit) that contained the facility's catchment area. Only district- and commune-level facilities had a value for this variable.
* **Commune**: The commune of Madagascar (3rd largest unit) that contained the facility's catchment area. Only basic health facility had a value for this variable.
* **FS**: The facility type and name. The facility type would typically be identified with an acronym (e.g., CSB2, CHD1, etc.), with the facility name following thereafter. The facility name would occasionally be the same as the commune, district, or region that corresponded with the facility's catchment area (e.g., CHRR Alaotra Mangoro). Some facilities were named for the village (*fokontany*) that they were located in. Other facilities were named for the groups that operated them (e.g., facilities named "EKAR" are operated by the *Eglizy Katôlika Apôstôlika Rômanina*, or the Roman Catholic Church).

@@

``` {r table_standardization_region_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

@@

After standardizing facility types and catchment areas, the sample consisted of `r  prettyNum(n_facilities_combined, big.mark = ",", scientific = FALSE)` unique facilities. This list of facilities was then manually inspected for any remaining duplicates. From reviewing this list, we observed that in the Diana region, the regional hospitals named "Hopitaly MANARA-PENITRA" and "Hopitaly Manara-Penitra Antsiranana" were duplicates, but appeared separately because the latter name contained the city the hospital is located in, Antsiranana. We standardized the names of those facilities, which resolved `r  prettyNum(n_dif, big.mark = ",", scientific = FALSE)` `r ifelse(n_dif > 1, "duplicates","duplicate")`).

@@

In order to systematically match facilities in our sample to facilities in the spatial inventory, we implemented an approximate string matching technique. This technique—also known as "fuzzy string searching"—is a common approach to record linkage, where information from one source (e.g., our sample) needs to be linked to data from another (e.g., the spatial inventory). As its name suggests, this techniques allows for "strings" of text to be matched approximately, rather than exactly, to corresponding patterns. In our case, this can be helpful if the facility name is spelled slightly differently in our sample versus the spatial inventory, due to typographic errors in the raw data or small orthographic variations (e.g., writing "2" as "II", inclusion or omission of a dash, etc.). A description of how this approach can be implemented in R is available at www.R-bloggers.com. @docFuzzyStringMatching2015

@@

In order to evaluate whether groups of two coordinates (which we referred to as "line groups") and groups of three or more coordinate ("polygon groups") were internally consistent (i.e., the points within a group were not geographically far apart, suggesting uncertainty in the location of a facility), we calculated the length (for line groups) and area (for polygon groups) of groups with more than one coordinate.

@@

```
\end{spacing}

>>>>

* **Region**: The region of Madagascar that contained the facility's catchment area. All facilities had a value for this variable.
* **District**: The district of Madagascar (2nd largest administrative unit) that contained the facility's catchment area. Only district- and commune-level facilities had a value for this variable.
* **Commune**: The commune of Madagascar (3rd largest unit) that contained the facility's catchment area. Only basic health facilities had a value for this variable.
* **FS**: The facility type and name. The facility type would typically be identified with an acronym (e.g., CSB2, CHD1, etc.), with the facility name following thereafter. The facility name would occasionally be the same as the commune, district, or region that corresponded with the facility's catchment area (e.g., CHRR Alaotra Mangoro). Some facilities were named for the village (*fokontany*) that they were located in. Other facilities were named for the groups that operated them (e.g., facilities named "EKAR" are operated by the *Eglizy Katôlika Apôstôlika Rômanina*, or the Roman Catholic Church).

@@

``` {r table_standardization_region_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}

@@

After standardizing facility types and catchment areas, the sample consisted of `r  prettyNum(n_facilities_combined, big.mark = ",", scientific = FALSE)` unique facilities. This list of facilities was then manually inspected for any remaining duplicates. From reviewing this list, we observed that in the Diana region, the regional hospitals named "Hopitaly MANARA-PENITRA" and "Hopitaly Manara-Penitra Antsiranana" were duplicates, but appeared separately because the latter name contained the city the hospital is located in, Antsiranana. We standardized the names of those facilities, which resolved `r  prettyNum(n_dif, big.mark = ",", scientific = FALSE)` `r ifelse(n_dif > 1, "duplicates","duplicate")`.

@@

In order to systematically match facilities in our sample to facilities in the spatial inventory, we implemented an approximate string matching technique. This technique—also known as "fuzzy string searching"—is a common approach to record linkage, where information from one source (i.e., our sample) needs to be linked to data from another (i.e., the spatial inventory). As its name suggests, this techniques allows for "strings" of text to be matched approximately, rather than exactly, to corresponding patterns. In our case, this can be helpful if the facility name is spelled slightly differently in our sample versus the spatial inventory, due to typographic errors in the raw data or small orthographic variations (e.g., writing "2" as "II", inclusion or omission of a dash, etc.). A description of how this approach can be implemented in R is available at www.R-bloggers.com. @docFuzzyStringMatching2015

@@

In order to evaluate whether groups of two coordinates (which we referred to as "line groups") and groups of three or more coordinates ("polygon groups") were internally consistent (i.e., the points within a group were not geographically far apart, suggesting uncertainty in the location of a facility), we calculated the length (for line groups) and area (for polygon groups) of groups with more than one coordinate.

@@

### 2023-05-11 conclusion.Rmd
Final revisions to manuscript

In Chapter 1, we examined how the global burden is defined, and we proposed an estimation approach to more comprehensively reflect morbidity and loss of life due to suicide and premature mortality attributable to mental disorders. After applying this composite estimation approach to the most recently available estimates from the Global Burden of Disease study, we found that approximately one in 6 disability-adjusted life years (approximately 16%) were due to mental disorders in 2019. We then applied a value of a statistical life year approach to estimate the associated global economic burden. Our findings suggest staggering loses: after accounting for premature mortality and other sources of morbidity associated with mental disorders, global losses were estimated to approximate 4.7 trillion \acr{USD} in 2019. The magnitude of these findings underscores the global scale of impact that mental disorders have and highlights the urgency for research and action to support mental health worldwide.

In Chapter 2, we examined how this global burden might be shifting with changes in climate by analyzing health system data in Madagascar, a country with little to no mental health surveillance data and high vulnerability to climate change. We obtained data on monthly counts of mental health related visits reported by 3,413 facilities in Madagascar from 2010 to 2020. We then geolocated these facilities and obtained meteorologic data on climate conditions to examine the impact of three climate change exposures—temperature, soil moisture, and duration of cyclones and tropical storms. We found that monthly mental health related visits declined as temperature increased, particularly in the central highlands, where cooler temperatures were more prevalent; conversely, higher grades of soil moisture were associated with greater mental health visits with a lag of approximately three months, an increase found primarily in regions associated with higher flood risk in Madagascar. Our findings illustrate potential heterogeneity in how changing climate conditions may impact mental health needs, and our work demonstrates how routine health system data may be leveraged to address data gaps in health surveillance, particularly in resource-constrained settings.

>>>>

In Chapter 1, we examined how the global burden is defined, and we proposed an estimation approach to more comprehensively reflect morbidity and loss of life due to suicide and premature mortality attributable to mental disorders. After applying this composite estimation approach to the most recently available estimates from the Global Burden of Disease study, we found that approximately one in 6 disability-adjusted life years (approximately 16%) were due to mental disorders in 2019. We then applied a value of a statistical life year approach to estimate the associated global economic burden. Our findings suggest staggering losses: after accounting for premature mortality and other sources of morbidity associated with mental disorders, global losses were estimated to approximate 4.7 trillion \acr{USD} in 2019. The magnitude of these findings underscores the global scale of impact that mental disorders have and highlights the urgency for research and action to support mental health worldwide.

In Chapter 2, we examined how this global burden might be shifting with changes in climate by analyzing health system data in Madagascar, a country with little to no mental health surveillance data and high vulnerability to climate change. We obtained data on monthly counts of mental health related visits reported by 3,413 facilities in Madagascar from 2010 to 2020. We then geolocated these facilities and obtained meteorologic data on climate conditions to examine the impact of three climate change exposures—temperature, soil moisture, and duration of cyclones and tropical storms. We found that monthly mental health related visits declined as temperature increased, particularly in the central highlands, where cooler temperatures were more prevalent; conversely, higher grades of soil moisture were associated with greater mental health visits with a lag of approximately three months, an increase found primarily in Madagascar's flood-prone regions. Our findings illustrate potential heterogeneity in how changing climate conditions may impact mental health needs, and our work demonstrates how routine health system data may be leveraged to address data gaps in health surveillance, particularly in resource-constrained settings.

### 2023-05-11 frontmatter.Rmd
Final revisions to manuscript

Jessica Cohen has been a constant source of joy and inspiration throughout my studies, and her teaching and scholarship have set a standard to aspire to. In addition to being a brilliant scholar, she is an incredible mentor and instructor, bringing genuine joy to the rigorous study of challenging questions. I feel extremely grateful to have learned so much from her example and from her enthusiasm for econometrics and public health.

@@

I am also deeply grateful to my coauthors and reviewers, whose thoughtful reflections strengthened every page. I thank Shekhar Saxena for his guiding leadership in global mental health and for welcoming me into the field when I first arrived at Harvard, and I thank Christopher Golden for welcoming me into his lab and providing every opportunity, guidance, and support a student could wish for throughout the development of the second paper of this thesis.

<!-- I also wish to express my gratitude to Judith Bass, who graciously offered to serve as the External Reader for this dissertation, and who fostered my interest in mental health while undertaking my Masters of Public Health degree at Johns Hopkins. -->

>>>>

Jessica Cohen has been a constant source of inspiration throughout my studies, and her teaching and scholarship have set a standard to aspire to. In addition to being a brilliant scholar, she is an incredible mentor and instructor, bringing genuine joy to the rigorous study of challenging questions. I feel extremely grateful to have learned so much from her example and from her enthusiasm for econometrics and public health.

@@

I am also deeply grateful to my coauthors and reviewers, whose thoughtful reflections strengthened every page. I thank Shekhar Saxena for his guiding leadership in global mental health and for welcoming me into the field when I first arrived at Harvard, and I thank Christopher Golden for welcoming me into his lab and providing every opportunity, guidance, and support a student could wish for throughout the development of the second paper of this thesis. I also wish to express my gratitude to Judith Bass, who graciously offered to serve as the External Reader for this dissertation.

### 2023-05-11 intro.Rmd
Final revisions to manuscript

Mental health is an essential part of human flourishing. As defined by the \acr{WHO}, it encompasses “a state of well-being in which every individual realizes [their] own potential, can cope with the normal stresses of life, can work productively and fruitfully, and is able to make a contribution to [their] community”.[@worldhealthorganizationComprehensiveMentalHealth2013]

@@

A better understanding of the evolving burden and dynamics of global mental health may thus have broad consequences to strengthening health system responses to mental disorders and improving health outcomes for millions of individuals worldwide. Contributing to such an understanding has motivated this dissertation, which takes as its focus different quantitative aspects of the global burden of mental illness—how we measure and evaluate it, how it may be changing, and how novel data sources may help in characterizing it, particularly in the absence of robust, high-frequency epidemiological surveillance. The papers presented in the subsequent three chapters echo the interdisciplinary nature of global mental health, drawing on a broad range of quantitative methods and applying analytic tools and insights from epidemiology, health economics, and econometrics. They further address different dimensions and determinants of population mental health, as illustrated in the conceptual framework shown in Figure \ref{figure_conceptual_framework}, which is based on a model identified by Dykxhoorn et al.[@dykxhoornConceptualisingPublicMental2022]

@@

In Chapter 1, we investigated the share of the global burden of disease attributable to mental disorders and its associated economic value. We reviewed recent efforts to estimate both the epidemiologic and economic burden of mental disorders, and we propose a composite approach to estimation to capture a broader share of attributable morbidity and mortality.[@bloomGlobalEconomicBurden2011; @charlsonExcessMortalityMental2015; @vigoEstimatingTrueGlobal2016; @vosGlobalBurden3692020a; @walkerMortalityMentalDisorders2015; @whitefordGlobalBurdenDisease2013] Applying this approach using the most recently available \acr{GBD} data, we estimated that the global burden of mental disorders is likely much higher than previously estimated, encompassing 16% of disability-adjusted life years in 2019. Using value of statistical life approaches, we estimated that the economic value of this burden would exceed 4.7 trillion \acr{USD}.

In Chapter 2, we investigated how health system visits for mental disorders in Madagascar may be shifting in respond to changes in climate. Madagascar has little to no mental health surveillance data and is among the nations most vulnerable to climate change. To address these gaps, we studied the impact of three climate change exposures—temperature, soil moisture, and duration of cyclones and tropical storms—by leveraging meteorologic, geospatial, and health system data reported by 3,413 facilities from 2010 to 2020. We found a statistically significant reduction in monthly mental health related visits associated with each degree Celcius increase in temperature, primarily localized to facilities in the central highlands, where cooler temperatures are more prevalent. We further found that higher soil moisture may be associated with more mental health visits in the future, after a three month lag; this increase was primarily found in the eastern lowlands and the northern dry deciduous forests, consistent with the geographic concentration of flood risk in Madagascar. Our findings point to potential heterogeneity in how changing climate conditions will impact mental health needs and system responses.

In Chapter 3, I investigated how internet search data for health symptoms might provide high frequency insight into the state of population mental health during the COVID-19 pandemic. Using search data from Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States, I explored how announcements of COVID-19 vaccine safety and efficacy data in November 2020 impacted Google search trends for mental health symptoms. I found evidence of statistically significant immediate and sustained declines in searches for anxiety, depression, and major depressive disorder throughout the 40 days following these announcements. The findings underscore the importance of timely and transparent communication and illustrate the potential application of high frequency internet search data for population mental health surveillance.

>>>>

Mental health is an essential part of human flourishing. As defined by the \acr{WHO}, it encompasses “a state of well-being in which every individual realizes [their] own potential, can cope with the normal stresses of life, can work productively and fruitfully, and is able to make a contribution to [their] community.”[@worldhealthorganizationComprehensiveMentalHealth2013]

@@

A better understanding of the evolving burden and dynamics of global mental health may thus have broad consequences to strengthening health system responses to mental disorders and improving health outcomes for millions of individuals worldwide.

Contributing to such an understanding has motivated this dissertation, which takes as its focus different quantitative aspects of the global burden of mental illness—how we measure and evaluate it, how it may be changing, and how novel data sources may help in characterizing it, particularly in the absence of robust, high-frequency epidemiological surveillance.

The three chapters presented in this dissertation reflect the interdisciplinary nature of global mental health, utilizing a diverse range of quantitative methods and drawing on insights from epidemiology, health economics, and econometrics. Furthermore, these papers align with the broader conceptual framework of population mental health (Figure \ref{figure_conceptual_framework}), which recognizes the complex interplay of environmental, social, and structural determinants in shaping mental health outcomes. This framework, based on determinants identified by Dykxhoorn et al.,[@dykxhoornConceptualisingPublicMental2022] illustrates the comprehensive contributions of these determinants to individual and public mental health and guides the approaches in Chapters 1, 2, and 3.

@@

In Chapter 1, we investigated the share of the global burden of disease attributable to mental disorders and its associated economic value. We reviewed recent efforts to estimate both the epidemiologic and economic burden of mental disorders, and we propose a composite approach to estimation to capture a broader share of attributable morbidity and mortality.[@bloomGlobalEconomicBurden2011; @charlsonExcessMortalityMental2015; @vigoEstimatingTrueGlobal2016; @vosGlobalBurden3692020a; @walkerMortalityMentalDisorders2015; @whitefordGlobalBurdenDisease2013] Applying this approach using the most recently available \acr{GBD} data, we estimated that the global burden of mental disorders is likely much higher than previously estimated, encompassing 16% of disability-adjusted life years in 2019. Using value of a statistical life approaches, we estimated that the economic value of this burden would exceed 4.7 trillion \acr{USD}.

In Chapter 2, we investigated how health system visits for mental disorders in Madagascar may be shifting in respond to changes in climate. Madagascar has little to no mental health surveillance data and is among the nations most vulnerable to climate change. To address these gaps, we studied the impact of three climate change exposures—temperature, soil moisture, and duration of cyclones and tropical storms—by leveraging meteorologic, geospatial, and health system data reported by 3,413 facilities from 2010 to 2020. We found a statistically significant reduction in monthly mental health related visits associated with each degree Celcius increase in temperature, primarily localized to facilities in the central highlands, where cooler temperatures are more prevalent. We further found that higher soil moisture may be associated with more mental health visits in the future, after a three-month lag; this increase was primarily found in the eastern lowlands and the northern dry deciduous forests, consistent with the geographic concentration of flood risk in Madagascar. Our findings point to potential heterogeneity in how changing climate conditions will impact mental health needs and system responses.

In Chapter 3, I investigated how internet search data for health symptoms might provide high-frequency insight into the state of population mental health during the COVID-19 pandemic. Using search data from Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States, I explored how announcements of COVID-19 vaccine safety and efficacy data in November 2020 impacted Google search trends for mental health symptoms. I found evidence of statistically significant immediate and sustained declines in searches for anxiety, depression, and major depressive disorder throughout the 40 days following these announcements. The findings underscore the importance of timely and transparent public health communication and illustrate the potential application of high-frequency internet search data for population mental health surveillance.

### 2023-05-11 paper1.Rmd
Final revisions to manuscript

@@

@@

Evaluating the economic burden of mental illness is a critical part in making the investment case for global mental health, informing public health decision-making, and guiding priority-setting and the scale up of much-needed interventions.[@chisholmScalingupTreatmentDepression2016] At the global level, however, the most recent estimate of the economic impact of mental disorders was published in 2011, using burden of disease estimates from 2004.[@bloomGlobalEconomicBurden2011] This landmark paper by Bloom and colleagues estimated that the value of losses due to mental disorders was roughly 1.3 trillion United States dollars (\acr{USD}) in 2010 (1.6 trillion \acr{USD} in 2019) when disability-adjusted life years (\acr{DALYs}) were valued at one times \acr{GDP} per capita.[@bloomGlobalEconomicBurden2011] The authors further projected that these losses would grow to nearly 2.5 trillion \acr{USD} 2010 (or approximately 3.0 trillion \acr{USD} in 2019) by 2030. (See Tables S1.1 and S1.2 in Appendix 1 for estimates from the other two approaches.) These estimates have been widely cited in calls to action concerning global mental health.[@patelLancetCommissionGlobal2018; @thelancetglobalhealthMentalHealthMatters2020]

@@

While \acr{GBD} remains the gold standard for global epidemiologic estimation, the nature of the \acr{GBD} scheme—in particular, the rationale for grouping certain conditions under mental disorders or not—has been the subject of debate in the literature.[@atunChallengesEstimatingTrue2016; @vigoEstimatingTrueGlobal2016; @whitefordChallengesEstimatingTrue2016] In particular, work by Vigo et al. (2016) published in \emph{The Lancet Psychiatry} argues for an expanded classification of mental disorders under the \acr{GBD} classification scheme to account for underestimation of the burden of mental disorders.[@vigoEstimatingTrueGlobal2016] The authors attribute this underestimation to five main causes: 1) the distinction drawn between mental and neurological diseases; 2) the categorization of self-harm and suicide under injuries; 3) the classification of all chronic pain and somatoform disorders under musculoskeletal disorders; 4) the exclusion of personality disorders; and 5) the exclusion of premature mortality due to mental disorders. Using data from the 2013 \acr{GBD} study, Vigo and colleagues re-allocated the entire burden of dementias, epilepsy, migraine, tension-type headache, and self-harm to mental disorders. In addition, a third of the burden of musculoskeletal disorders without anatomical correlate (i.e., somatoform disorders with prominent pain) was attributed to mental disorders.[@vigoEstimatingTrueGlobal2016] This reallocation attributed 13% of \acr{DALYs} to mental disorders, a 6 percentage point increase from the \acr{GBD} estimate of 7%.

@@

\addcontentsline{lot}{table}{Table 1.1: Comparison of the composition of the global burden of mental disorders, by estimation approach.}

@@

```
\end{raggedright}

@@

Put in context of the existing literature, our epidemiological and economic estimates provide two important contributions. First, our findings echo in magnitude those of Vigo and colleagues,[@vigoEstimatingTrueGlobal2016] which have highlighted that suicide and premature mortality due to mental disorders are potentially large sources of underestimation in the current \acr{GBD} classification. Second, when including these sources of attributable mortality, the economic findings suggest staggering loses. `r discussion_sentence3`[@bloomGlobalEconomicBurden2011]

>>>>

\vspace{5pt}

@@

\vspace{1pt}

@@

Evaluating the economic burden of mental illness is a critical part in making the investment case for global mental health, informing public health decision-making, and guiding priority-setting and the scale-up of much-needed interventions.[@chisholmScalingupTreatmentDepression2016] At the global level, however, the most recent estimate of the economic impact of mental disorders was published in 2011, using burden of disease estimates from 2004.[@bloomGlobalEconomicBurden2011] This landmark paper by Bloom and colleagues estimated that the value of losses due to mental disorders was roughly 1.3 trillion United States dollars (\acr{USD}) in 2010 (1.6 trillion \acr{USD} in 2019) when disability-adjusted life years (\acr{DALYs}) were valued at one times \acr{GDP} per capita.[@bloomGlobalEconomicBurden2011] The authors further projected that these losses would grow to nearly 2.5 trillion \acr{USD} 2010 (or approximately 3.0 trillion \acr{USD} in 2019) by 2030. (See Tables S1.1 and S1.2 in Appendix 1 for estimates from the other two approaches.) These estimates have been widely cited in calls to action concerning global mental health.[@patelLancetCommissionGlobal2018; @thelancetglobalhealthMentalHealthMatters2020]

@@

While \acr{GBD} remains the gold standard for global epidemiologic estimation, the nature of the \acr{GBD} scheme—in particular, the rationale for grouping certain conditions under mental disorders or not—has been the subject of debate in the literature.[@atunChallengesEstimatingTrue2016; @vigoEstimatingTrueGlobal2016; @whitefordChallengesEstimatingTrue2016] In particular, work by Vigo et al. (2016) published in \emph{The Lancet Psychiatry} argues for an expanded classification of mental disorders under the \acr{GBD} classification scheme to account for underestimation of the burden of mental disorders.[@vigoEstimatingTrueGlobal2016] The authors attribute this underestimation to five main causes: 1) the distinction drawn between mental and neurological diseases; 2) the categorization of self-harm and suicide under injuries; 3) the classification of all chronic pain and somatoform disorders under musculoskeletal disorders; 4) the exclusion of personality disorders; and 5) the exclusion of premature mortality due to mental disorders. Using data from the 2013 \acr{GBD} study, Vigo and colleagues re-allocated the entire burden of dementia, epilepsy, migraine, tension-type headache, and self-harm to mental disorders. In addition, a third of the burden of musculoskeletal disorders without anatomical correlate (i.e., somatoform disorders with prominent pain) was attributed to mental disorders.[@vigoEstimatingTrueGlobal2016] This reallocation attributed 13% of \acr{DALYs} to mental disorders, a 6 percentage point increase from the \acr{GBD} estimate of 7%.

@@

@@

```
\addcontentsline{lot}{table}{Table 1.1: Comparison of the composition of the global burden of mental disorders, by estimation approach.}

@@

Put in context of the existing literature, our epidemiological and economic estimates provide two important contributions. First, our findings echo in magnitude those of Vigo and colleagues,[@vigoEstimatingTrueGlobal2016] which have highlighted that suicide and premature mortality due to mental disorders are potentially large sources of underestimation in the current \acr{GBD} classification. Second, when including these sources of attributable mortality, the economic findings suggest staggering losses. `r discussion_sentence3`[@bloomGlobalEconomicBurden2011]
